Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Remove apology paragraph

Initially, we had intended to build a tool for studying large memory systems.
We found that the first step in doing so is studying the scalability of current
memory management systems themselves. Thus, our related work section, while
still relevant to our overall goal, is more directed at the second step of
building the tool.

>>>>

%Initially, we had intended to build a tool for studying large memory systems.
%We found that the first step in doing so is studying the scalability of current
%memory management systems themselves. Thus, our related work section, while
%still relevant to our overall goal, is more directed at the second step of
%building the tool.
